Simulation Results

### 2020-05-10 Simulation Results/Simulation Results.Rmd
ppp updates

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
library(tidyverse); options(tibble.width = Inf); theme_set(theme_bw())
library(magrittr)
library(here)
```

@@

files <- logistic_regression_bench_files

@@

exp_gamma_results <- exp_gamma_bench_files %>% 
  combine_bench_indiv("exponential_gamma")
normal_gamma_tau_results <- normal_gamma_tau_bench_files %>%
  combine_bench_indiv("normal_gamma_tau")
normal_normal_results <- normal_normal_bench_files %>%
  combine_bench_indiv("normal_normal")
beta_bernoulli_results <- beta_bernoulli_bench_files %>%
  combine_bench_indiv("beta_bernoulli")
beta_binomial_results <- beta_binomial_bench_files %>%
  combine_bench_indiv("beta_binomial")
poisson_gamma_results <- poisson_gamma_bench_files %>%
  combine_bench_indiv("poisson_gamma")
hier_beta_binomial_results <- hierarchical_beta_binomial_bench_files %>%
  combine_bench_indiv("hierarchical_beta_binomial")
hier_full_bb_results <- hierarchical_full_beta_binomial_bench_files %>%
  combine_bench_indiv("hierarchical_full_beta_binomial")
hier_log_reg_results <- hierarchical_logistic_regression_bench_files %>%
  combine_bench_indiv("hierarchical_logistic_regression")
linear_reg_results <- linear_regression_bench_files %>% 
  combine_bench_indiv("linear regression")
logistic_reg_results <- logistic_regression_bench_files %>% 
  combine_bench_indiv("logistic regression")
poisson_reg_results <- poisson_regression_bench_files %>% 
  combine_bench_indiv("poisson regression")

@@

bench_results_indiv <- bind_rows(
  exp_gamma_results,
  normal_gamma_tau_results,
  normal_normal_results,
  beta_bernoulli_results, 
  beta_binomial_results,
  poisson_gamma_results,
  hier_beta_binomial_results,
  hier_full_bb_results,
  hier_log_reg_results,
  linear_reg_results,
  logistic_reg_results,
  poisson_reg_results
)

@@

```{r}
bench_results_indiv <- readRDS(here("bench_results_indiv2.RDS"))

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
theme_set(theme_minimal())
library(magrittr)
library(here)
```

@@

eight_schools_bench_files <- c(
  here("Simulation Results", "8-schools", "eight-schools-results.rds"),
  here("Simulation Results", "8-schools", "eight-schools-results-stan.rds")
)

ma_model_bench_files <- c(
  here("Simulation Results", "time-series", "ma-model", "ma-model-results.rds"),
  here("Simulation Results", "time-series", "ma-model", "ma-model-results-stan.rds")
)

ar_model_bench_files <- c(
  here("Simulation Results", "time-series", "ar-model", "ar-model-results-no-nimble.rds"),
  here("Simulation Results", "time-series", "ar-model", "ar-model-results-greta.rds"),
  here("Simulation Results", "time-series", "ar-model", "ar-model-stan-compile-results.rds")
)

files <- eight_schools_bench_files

model_name <- "8"

@@

exp_gamma_results <- exp_gamma_bench_files %>% 
  combine_bench_indiv("exponential_gamma")
normal_gamma_tau_results <- normal_gamma_tau_bench_files %>%
  combine_bench_indiv("normal_gamma_tau")
normal_normal_results <- normal_normal_bench_files %>%
  combine_bench_indiv("normal_normal")
beta_bernoulli_results <- beta_bernoulli_bench_files %>%
  combine_bench_indiv("beta_bernoulli")
beta_binomial_results <- beta_binomial_bench_files %>%
  combine_bench_indiv("beta_binomial")
poisson_gamma_results <- poisson_gamma_bench_files %>%
  combine_bench_indiv("poisson_gamma")
hier_beta_binomial_results <- hierarchical_beta_binomial_bench_files %>%
  combine_bench_indiv("hierarchical_beta_binomial")
hier_full_bb_results <- hierarchical_full_beta_binomial_bench_files %>%
  combine_bench_indiv("hierarchical_full_beta_binomial")
hier_log_reg_results <- hierarchical_logistic_regression_bench_files %>%
  combine_bench_indiv("hierarchical_logistic_regression")
linear_reg_results <- linear_regression_bench_files %>% 
  combine_bench_indiv("linear regression")
logistic_reg_results <- logistic_regression_bench_files %>% 
  combine_bench_indiv("logistic regression")
poisson_reg_results <- poisson_regression_bench_files %>% 
  combine_bench_indiv("poisson regression")
cox_exp_results <- cox_exponential_bench_files %>% 
  combine_bench_indiv("cox exponential")
eight_schools_results <- eight_schools_bench_files %>% 
  combine_bench_indiv("eight schools")
ma_model_results <- ma_model_bench_files %>% 
  combine_bench_indiv("ma model")
ar_model_results <- ar_model_bench_files %>% 
  combine_bench_indiv("ar model")

@@

bench_results_indiv <- bind_rows(
  exp_gamma_results,
  normal_gamma_tau_results,
  normal_normal_results,
  beta_bernoulli_results, 
  beta_binomial_results,
  poisson_gamma_results,
  hier_beta_binomial_results,
  hier_full_bb_results,
  hier_log_reg_results,
  linear_reg_results,
  logistic_reg_results,
  poisson_reg_results,
  cox_exp_results,
  eight_schools_results,
  ma_model_results,
  ar_model_results
)

@@

```{r}
bench_results_indiv <- readRDS(here("bench_results_indiv.RDS"))

@@

## Strip Charts

```{r}
bench_results_indiv %>% 
  mutate(model = model_name %>% 
           str_replace_all("_", " ")) %>% 
  ggplot(aes(method, time)) + 
  geom_jitter(width = 0.1) + 
  facet_wrap(vars(model)) + 
  theme_update(panel.grid.minor = element_blank()) + 
  scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan",  "Nimble", "Greta", "Stan Compile")) + 
  ylim(0,100)

bench_results_indiv %>% 
  mutate(model = model_name %>% 
           str_replace_all("_", " ")) %>% 
  # filter(time < 100) %>% 
  ggplot(aes(method, time, color = method)) + 
  geom_jitter(width = 0.1) + 
  facet_wrap(vars(model), scales = "free_y") + 
  theme_update(panel.grid.minor = element_blank()) + 
  scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan",  "Nimble", "Greta", "Stan Compile"))

- First slide of strip charts
```{r}
first_eight <- bench_results_indiv %>% 
  mutate(model = model_name %>% 
           str_replace_all("_", " ")) %>% 
  group_by(model) %>% 
  summarize(mean_time = mean(time)) %>% 
  arrange(mean_time) %>% 
  pull(model) %>% 
  .[1:8] %>% 
  sort()

first_six <- bench_results_indiv %>% 
  mutate(model = model_name %>% 
           str_replace_all("_", " ")) %>% 
  group_by(model) %>% 
  summarize(mean_time = mean(time)) %>% 
  arrange(mean_time) %>% 
  pull(model) %>% 
  .[1:6] %>% 
  sort()

bench_results_indiv %>% 
  mutate(model = model_name %>% 
           str_replace_all("_", " ")) %>% 
  filter(model %in% first_eight) %>% 
  filter(time < 100) %>% 
  ggplot(aes(method, time, color = method)) + 
  geom_jitter(width = 0.2, size = 1) + 
  # facet_wrap(vars(model), scales = "free_y") + 
  facet_wrap(vars(model)) + 
  theme_update(panel.grid.minor = element_blank()) + 
  scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan",  "Nimble", "Greta", "Stan Compile"))

bench_results_indiv %>% 
  mutate(model = model_name %>% 
           str_replace_all("_", " ")) %>% 
  filter(model %in% first_six) %>% 
  filter(time < 100) %>% 
  ggplot(aes(method, time, color = method)) + 
  geom_jitter(width = 0.2) + 
  # facet_wrap(vars(model), scales = "free_y") + 
  facet_wrap(vars(model)) + 
  theme_update(panel.grid.minor = element_blank()) + 
  scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan",  "Nimble", "Greta", "Stan Compile"))

@@

## Strip charts for accuracy

```{r}
time_results
```
